\bibitem{2022Kim}Kim, Y., Lee, J., Pititto, A., Falco, L., Lee, M., Yoon, K. \& Cho, I. Maritime Traffic Evaluation Using Spatial-Temporal Density Analysis Based on Big AIS Data. {\em Applied Sciences}. \textbf{12} (2022)
\bibitem{2013Kazemi}Kazemi, S., Abghari, S., Lavesson, N., Johnson, H. \& Ryman, P. Open data for anomaly detection in maritime surveillance. {\em Expert Systems With Applications}. \textbf{40}, 5719-5729 (2013)
\bibitem{2017Sfyridis}Sfyridis, A., Cheng, T. \& Vespe, M. Detecting vessels carrying migrants using machine learning. {\em ISPRS Annals Of Photogrammetry, Remote Sensing And Spatial Information Sciences}. \textbf{IV-4/W2} pp. 53-60 (2017,10)
\bibitem{2018Dogru}Dogru, N. \& Subasi, A. Traffic accident detection using random forest classifier. {\em 2018 15th Learning And Technology Conference (L\&T)}. pp. 40-45 (2018)
\bibitem{ZHANG2021107674}Zhang, M., Montewka, J., Manderbacka, T., Kujala, P. \& Hirdaris, S. A Big Data Analytics Method for the Evaluation of Ship - Ship Collision Risk reflecting Hydrometeorological Conditions. {\em Reliability Engineering \& System Safety}. \textbf{213} pp. 107674 (2021)
\bibitem{2009Chandola}Chandola, V., Banerjee, A. \& Kumar, V. Anomaly Detection: A Survey. {\em ACM Comput. Surv.}. \textbf{41} (2009,7)
\bibitem{2011Martineau}Martineau, E. \& Roy, J. Maritime Anomaly Detection: Domain Introduction and Review of Selected Literature. {\em DEFENCE RESEARCH AND DEVELOPMENT CANADA VALCARTIER (QUEBEC)}. (2011,1)
\bibitem{2008Roy}Roy, J. Anomaly detection in the maritime domain. {\em Proc SPIE}. (2008,5)
\bibitem{2014Mascaro}Mascaro, S., Nicholso, A. \& Korb, K. Anomaly detection in vessel tracks using Bayesian networks. {\em International Journal Of Approximate Reasoning}. \textbf{55} pp. 84-98 (2014,1)
\bibitem{2008Laxhammar}Laxhammar, R. Anomaly detection for sea surveillance. {\em 2008 11th International Conference On Information Fusion}. pp. 1-8 (2008,6)
\bibitem{BOUEJLA201422}Bouejla, A., Chaze, X., Guarnieri, F. \& Napoli, A. A Bayesian network to manage risks of maritime piracy against offshore oil fields. {\em Safety Science}. \textbf{68} pp. 222-230 (2014)
\bibitem{2018dAfflisio}D'Afflisio, E., Braca, P., Millefiori, L. \& Willett, P. Maritime Anomaly Detection Based on Mean-Reverting Stochastic Processes Applied to a Real-World Scenario. {\em 2018 21st International Conference On Information Fusion (FUSION)}. (2018,7)
\bibitem{2018dAfflisio1}D'Afflisio, E., Braca, P., Millefiori, L. \& Willett, P. Detecting Anomalous Deviations From Standard Maritime Routes Using the Ornstein-Uhlenbeck Process. {\em IEEE Transactions On Signal Processing}. \textbf{66}, 6474-6487 (2018)
\bibitem{2020Loi}Loi, N., Trung, K., Hop, T., Thanh, S. \& Khuong, N. Abnormal Moving Speed Detection Using Combination of Kernel Density Estimator and DBSCAN for Coastal Surveillance Radars. {\em 2020 7th International Conference On Signal Processing And Integrated Networks (SPIN)}. pp. 143-147 (2020)
\bibitem{2018Forti}Forti, N., Millefiori, L. \& Braca, P. Hybrid Bernoulli Filtering for Detection and Tracking of Anomalous Path Deviations. {\em 2018 21st International Conference On Information Fusion (FUSION)}. (2018,7)
\bibitem{2019Forti}Forti, N., Millefiori, L., Braca, P. \& Willett, P. Anomaly Detection and Tracking Based on Mean-Reverting Processes with Unknown Parameters. {\em ICASSP 2019 - 2019 IEEE International Conference On Acoustics, Speech And Signal Processing (ICASSP)}. (2019,5)
\bibitem{2020Forti}Forti, N., Millefiori, L., Braca, P. \& Willett, P. Random Finite Set Tracking for Anomaly Detection in the Presence of Clutter. {\em 2020 IEEE Radar Conference (RadarConf20)}. pp. 1-6 (2020)
\bibitem{2022Forti}Forti, N., D'Afflisio, E., Braca, P., Millefiori, L., Willett, P. \& Carniel, S. Maritime Anomaly Detection in a Real-World Scenario: Ever Given Grounding in the Suez Canal. {\em IEEE Transactions On Intelligent Transportation Systems}. \textbf{23}, 13904-13910 (2022)
\bibitem{2022Forti1}Forti, N., Millefiori, L., Braca, P. \& Willett, P. Bayesian Filtering for Dynamic Anomaly Detection and Tracking. {\em IEEE Transactions On Aerospace And Electronic Systems}. \textbf{58} (2022,6)
\bibitem{2022Forti2}Forti, N., D'Afflisio, E., Braca, P., Millefiori, L., Carniel, S. \& Willett, P. Next-Gen Intelligent Situational Awareness Systems for Maritime Surveillance and Autonomous Navigation [Point of View]. {\em Proceedings Of The IEEE}. \textbf{110} (2022,10)
\bibitem{2019Milios}Milios, A., Bereta, K., Chatzikokolakis, K., Zissis, D. \& Matwin, S. Automatic Fusion of Satellite Imagery and AIS data for Vessel Detection. {\em 2019 22th International Conference On Information Fusion (FUSION)}. pp. 1-5 (2019)
\bibitem{2019Fahn}Fahn, C., Ling, J., Yeh, M., Huang, P. \& Wu, M. Abnormal Maritime Activity Detection in Satellite Image Sequences Using Trajectory Features. {\em International Journal Of Future Computer And Communication}. \textbf{8} pp. 29-33 (2019,3)
\bibitem{fiorini2016ais}Fiorini, M., Capata, A. \& Bloisi, D. AIS data visualization for maritime spatial planning (MSP). {\em International Journal Of E-Navigation And Maritime Economy}. \textbf{5} pp. 45-60 (2016)
\bibitem{2016Ning}Ning, J. Study on Maritime traffic density calculation and maritime hotspots discovery based on AIS data. {\em Special Issue Of Applied Sciences "Transportation Big Data And Its Applications", Section "Computing And Artificial Intelligence"}. (2016,5)
\bibitem{2008Ristic}Ristic, B., La, S., Morelande, M. \& Gordon, N. Statistical analysis of motion patterns in AIS Data: Anomaly detection and motion prediction. {\em 2008 11th International Conference On Information Fusion}. pp. 1-7 (2008)
\bibitem{2018Riveiro}Riveiro, M., Pallotta, G. \& Vespe, M. Maritime anomaly detection: A review. {\em Wiley Interdisciplinary Reviews: Data Mining And Knowledge Discovery}. \textbf{8} (2018,5)
\bibitem{2015Anneken}Anneken, M., Fischer, Y. \& Beyerer, J. Evaluation and comparison of anomaly detection algorithms in annotated datasets from the maritime domain. {\em 2015 SAI Intelligent Systems Conference (IntelliSys)}. pp. 169-178 (2015)
\bibitem{DABROWSKI2015116}Dabrowski, J. \& Villiers, J. Maritime piracy situation modelling with dynamic Bayesian networks. {\em Information Fusion}. \textbf{23} pp. 116-130 (2015)
\bibitem{2009Laxhammar}Laxhammar, R., Falkman, G. \& Sviestins, E. Anomaly detection in sea traffic - A comparison of the Gaussian Mixture Model and the Kernel Density Estimator. {\em 2009 12th International Conference On Information Fusion}. pp. 756-763 (2009,8)
\bibitem{2002Kraiman}Kraiman, J., Arouh, S. \& Webb, M. Automated anomaly detection processor. {\em Proceedings Of SPIE - The International Society For Optical Engineering}. \textbf{4716} pp. 128-137 (2002,7)
\bibitem{2008Riveiro1}Riveiro, M., Johansson, F., Falkman, G. \& Ziemke, T. Supporting Maritime Situation Awareness Using Self Organizing Maps and Gaussian Mixture Models.. {\em Proceedings Of The 2008 Conference On Tenth Scandinavian Conference On Artificial Intelligence: SCAI 2008}. \textbf{173} pp. 84-91 (2008,1)
\bibitem{2013Pallotta}Pallotta, G., Vespe, M. \& Bryan, K. Vessel Pattern Knowledge Discovery from AIS Data: A Framework for Anomaly Detection and Route Prediction. {\em Entropy}. \textbf{15}, 2218-2245 (2013,6)
\bibitem{2013Pallotta1}Pallotta, G., Vespe, M. \& Bryan, K. Traffic knowledge discovery from AIS data. {\em Proceedings Of The 16th International Conference On Information Fusion}. pp. 1996-2003 (2013)
\bibitem{2018Marzuki}Marzuki, M., Gaspar, P., Garello, R., Kerbaol, V. \& Fablet, R. Fishing Gear Identification From Vessel-Monitoring-System-Based Fishing Vessel Trajectories. {\em IEEE Journal Of Oceanic Engineering}. \textbf{43}, 689-699 (2018)
\bibitem{Le2016TrajectoryPO}Le, Q. \& Zheng, Z. Trajectory Prediction of Vessels based on Data Mining and Machine Learning. {\em Journal Of Digital Information Management}. \textbf{14}, 33-40 (2016)
\bibitem{2022Wei}Wei, Z., Xie, X. \& Zhang, X. Maritime anomaly detection based on a support vector machine. {\em Soft Computing}. \textbf{26} (2022,8)
\bibitem{2015Shahir}Shahir, H., Glasser, U., Shahir, A. \& Wehn, H. Maritime situation analysis framework: Vessel interaction classification and anomaly detection. {\em 2015 IEEE International Conference On Big Data (Big Data)}. (2015,10)
\bibitem{2016Jiang}Jiang, X., Silver, D., Hu, B. \& Souza, E. Fishing Activity Detection from AIS Data Using Autoencoders. {\em Canadian Conference On Artificial Intelligence}. pp. 33-39 (2016,5)
\bibitem{2013Handayani}Handayani, D., Sediono, W. \& Shah, A. Anomaly Detection in Vessel Tracking Using Support Vector Machines (SVMs). {\em 2013 International Conference On Advanced Computer Science Applications And Technologies}. pp. 213-217 (2013)
\bibitem{2020Singh}Singh, S. \& Heymann, F. Machine Learning-Assisted Anomaly Detection in Maritime Navigation using AIS Data. {\em 2020 IEEE/ION Position, Location And Navigation Symposium (PLANS)}. pp. 832-838 (2020)
\bibitem{2020Arasteh}Arasteh, S., Tayebi, M., Zohrevand, Z., Glasser, U., Shahir, A., Saeedi, P. \& Wehn, H. Fishing Vessels Activity Detection from Longitudinal AIS Data. {\em Proceedings Of The 28th International Conference On Advances In Geographic Information Systems}. pp. 347-356 (2020)
\bibitem{2023Chen2}Chen, Q., Xie, L., Zeng, L., Jiang, S., Ding, W., Huang, X. \& Wang, H. Neighborhood Rough Residual Network-Based Outlier Detection Method in IoT-Enabled Maritime Transportation Systems. {\em IEEE Transactions On Intelligent Transportation Systems}. (2023)
\bibitem{2019Young}Young, D. Deep Nets Spotlight Illegal, Unreported, Unregulated (IUU) Fishing. {\em 2019 IEEE Applied Imagery Pattern Recognition Workshop (AIPR)}. pp. 1-7 (2019)
\bibitem{2022Djenouri}Djenouri, Y., Belhadi, A., Djenouri, D., Srivastava, G. \& Lin, J. Intelligent Deep Fusion Network for Anomaly Identification in Maritime Transportation Systems. {\em IEEE Transactions On Intelligent Transportation Systems}. pp. 1-9 (2022)
\bibitem{CHEN2020108182}Chen, X., Liu, Y., Achuthan, K. \& Zhang, X. A ship movement classification based on Automatic Identification System (AIS) data using Convolutional Neural Network. {\em Ocean Engineering}. \textbf{218} pp. 108182 (2020)
\bibitem{2019Freitas}Freitas, S., Silva, H., Almeida, J. \& Silva, E. Convolutional neural network target detection in hyperspectral imaging for maritime surveillance. {\em International Journal Of Advanced Robotic Systems}. \textbf{16}, 172988141984299 (2019,5)
\bibitem{2022Czaplewski}Czaplewski, B. \& Dzwonkowski, M. A novel approach exploiting properties of convolutional neural networks for vessel movement anomaly detection and classification. {\em ISA Transactions}. \textbf{119} pp. 1-16 (2022,1)
\bibitem{2018Kroodsma}Kroodsma, D., Mayorga, J., Hochberg, T., Miller, N., Boerder, K., Ferretti, F., Wilson, A., Bergman, B., White, T., Block, B., Woods, P., Sullivan, B., Costello, C. \& Worm, B. Tracking the Global Footprint of Fisheries. {\em Science}. \textbf{359} (2018,2)
\bibitem{2019Ma}Ma, C., Zhenjiang, M., Min, L., Shaoyue, S. \& Yang, M. Detecting Anomalous Trajectories via Recurrent Neural Networks. {\em Computer Vision - ACCV 2018 - 14th Asian Conference On Computer Vision, Revised Selected Papers}. pp. 370-382 (2019)
\bibitem{2019Mantecon}Mantecon, T., Casals, D., Navarro Corcuera, J., Blanco, C. \& Jaureguizar, F. Deep Learning to Enhance Maritime Situation Awareness. {\em 2019 20th International Radar Symposium (IRS)}. (2019,6)
\bibitem{2018Ljunggren}Ljunggren, H. Using Deep Learning for Classifying Ship Trajectories. {\em 2018 21st International Conference On Information Fusion (FUSION)}. pp. 2158-2164 (2018)
\bibitem{2019Hoque}Hoque, X. \& Sharma, S. Ensembled Deep Learning Approach for Maritime Anomaly Detection System. {\em Proceedings Of ICETIT 2019}. pp. 862-869 (2019,9)
\bibitem{zhaoshi2019}Zhao, L. \& Shi, G. Maritime Anomaly Detection using Density-based Clustering and Recurrent Neural Network. {\em The Journal Of Navigation}. \textbf{72}, 894-916 (2019)
\bibitem{2021Karatas}Karatas, G., Karagoz, P. \& Ayran, O. Trajectory pattern extraction and anomaly detection for maritime vessels. {\em Internet Of Things}. \textbf{16} pp. 100436 (2021,12)
\bibitem{2019Li}Li, H., Chen, L., Li, F. \& Huang, M. Ship detection and tracking method for satellite video based on multiscale saliency and surrounding contrast analysis. {\em Journal Of Applied Remote Sensing}. \textbf{13} pp. 1 (2019,6)
\bibitem{2019Liang}Liang, M., Liu, R., Zhong, Q., Liu, J. \& Zhang, J. Neural Network-Based Automatic Reconstruction of Missing Vessel Trajectory Data. {\em 2019 IEEE 4th International Conference On Big Data Analytics (ICBDA)}. (2019,3)
\bibitem{2021Mehri}Mehri, S., Alesheikh, A. \& Basiri, A. A Contextual Hybrid Model for Vessel Movement Prediction. {\em IEEE Access}. \textbf{9} (2021)
\bibitem{2023Mehri}Mehri, S., Alesheikh, A. \& Basiri, A. A context-aware approach for vessels' trajectory prediction. {\em Ocean Engineering}. \textbf{282} pp. 114916 (2023,8)
\bibitem{2023Wang}Wang, Y., Liu, J., Liu, R., Wu, W. \& Liu, Y. Interval prediction of vessel trajectory based on lower and upper bound estimation and attention-modified LSTM with bayesian optimization. {\em Physica A: Statistical Mechanics And Its Applications}. \textbf{630} pp. 129275 (2023,11)
\bibitem{2018Nguyen}Nguyen, D., Vadaine, R., Hajduch, G., Garello, R. \& Fablet, R. A Multi-Task Deep Learning Architecture for Maritime Surveillance Using AIS Data Streams. {\em 2018 IEEE 5th International Conference On Data Science And Advanced Analytics (DSAA)}. (2018,10)
\bibitem{2020Nguyen}Nguyen, D., Simonin, M., Hajduch, G., Vadaine, R., Tedeschi, C. \& Fablet, R. Detection of Abnormal Vessel Behaviours from AIS data using GeoTrackNet: from the Laboratory to the Ocean. {\em 2020 21st IEEE International Conference On Mobile Data Management (MDM)}. (2020,8)
\bibitem{2022Nguyen}Nguyen, D., Vadaine, R., Hajduch, G., Garello, R. \& Fablet, R. GeoTrackNet - A Maritime Anomaly Detector Using Probabilistic Neural Network Representation of AIS Tracks and A Contrario Detection. {\em IEEE Transactions On Intelligent Transportation Systems}. \textbf{23}, 5655-5667 (2022)
\bibitem{2021Eljabu}Eljabu, L., Etemad, M. \& Matwin, S. Anomaly Detection in Maritime Domain based on Spatio-Temporal Analysis of AIS Data Using Graph Neural Networks. {\em 2021 5th International Conference On Vision, Image And Signal Processing (ICVISP)}. (2021,12)
\bibitem{2022Liu5}Liu, H., Liu, Y. \& Zong, Z. Research on Ship Abnormal Behavior Detection Method Based on Graph Neural Network. {\em 2022 IEEE International Conference On Mechatronics And Automation (ICMA)}. (2022,8)
\bibitem{2021Magnussen}Magnussen, B., Bläser, N., Jensen, R. \& Ylänen, K. Destination Prediction of Oil Tankers Using Graph Abstractions and Recurrent Neural Networks. {\em Computational Logistics}. (2021)
\bibitem{2022Singh}Singh, S., Fowdur, J., Gawlikowski, J. \& Medina, D. Leveraging Graph and Deep Learning Uncertainties to Detect Anomalous Maritime Trajectories. {\em IEEE Transactions On Intelligent Transportation Systems}. \textbf{23} (2022,12)
\bibitem{2006Bomberger}Bomberger, N., Rhodes, B., Seibert, M. \& Waxman, A. Associative Learning of Vessel Motion Patterns for Maritime Situation Awareness. {\em 2006 9th International Conference On Information Fusion}. (2006,7)
\bibitem{2005Rhodes}Rhodes, B., Bomberger, N., Seibert, M. \& Waxman, A. Maritime situation monitoring and awareness using learning mechanisms. {\em MILCOM 2005 - 2005 IEEE Military Communications Conference}. \textbf{1} pp. 646-652 (2005)
\bibitem{2018Kawaguchi}Kawaguchi, Y. Anomaly Detection Based on Feature Reconstruction from Subsampled Audio Signals. {\em 2018 26th European Signal Processing Conference (EUSIPCO)}. pp. 2524-2528 (2018)
\bibitem{2018Tu}Tu, E., Zhang, G., Rachmawati, L., Rajabally, E. \& Huang, G. Exploiting AIS Data for Intelligent Maritime Navigation: A Comprehensive Survey From Data to Methodology. {\em IEEE Transactions On Intelligent Transportation Systems}. \textbf{19}, 1559-1582 (2018)
\bibitem{2020Zhang}Zhang, B., Ren, H., Wang, P. \& Wang, D. Research Progress on Ship Anomaly Detection Based on Big Data. {\em 2020 IEEE 11th International Conference On Software Engineering And Service Science (ICSESS)}. pp. 316-320 (2020)
\bibitem{2023Gamage}Gamage, C., Dinalankara, D., Samarabandu, J. \& Subasinghe, A. A comprehensive survey on the applications of machine learning techniques on maritime surveillance to detect abnormal maritime vessel behaviors. {\em WMU Journal Of Maritime Affairs}. (2023,6)
\bibitem{2023Stach}Stach, T., Kinkel, Y., Constapel, M. \& Burmeister, H. Maritime Anomaly Detection for Vessel Traffic Services: A Survey. {\em Journal Of Marine Science And Engineering}. \textbf{11} (2023)
\bibitem{2020MayPetry}May Petry, L., Soares, A., Bogorny, V., Brandoli, B. \& Matwin, S. Challenges in Vessel Behavior and Anomaly Detection: From Classical Machine Learning to Deep Learning. {\em Lecture Notes In Computer Science}.
\bibitem{2021Dogancay}Dogancay, K., Tu, Z. \& Ibal, G. Research into vessel behaviour pattern recognition in the maritime domain: Past, present and future. {\em Digital Signal Processing}. \textbf{119} pp. 103191 (2021,12)
\bibitem{2022Cao}Cao, P., Zhong, R. \& Huang, W. Anomalous Trajectory Detection Using Masked Autoregressive Flow Considering Route Choice Probability. {\em Journal Of Advanced Transportation}. \textbf{2022} (2022,10)
\bibitem{2019Bouritsas}Bouritsas, G., Daveas, S., Danelakis, A. \& Thomopoulos, S. Automated Real-time Anomaly Detection in Human Trajectories using Sequence to Sequence Networks. {\em Proc. IEEE Int. Conf. On Advanced Video And Signal-Based Surveillance (AVSS)}. pp. 1-8 (2019,9)
\bibitem{2018FernandezArguedas}Fernandez Arguedas, V., Pallotta, G. \& Vespe, M. Maritime Traffic Networks: From Historical Positioning Data to Unsupervised Maritime Traffic Monitoring. {\em IEEE Transactions On Intelligent Transportation Systems}. \textbf{19}, 722-732 (2018)
\bibitem{Varlamis2019ANA}Varlamis, I., Tserpes, K., Etemad, M., Junior, A. \& Matwin, S. A Network Abstraction of Multi-vessel Trajectory Data for Detecting Anomalies. {\em EDBT/ICDT Workshops}. (2019)
\bibitem{bloisi2016enhancing}Bloisi, D., Previtali, F., Pennisi, A., Nardi, D. \& Fiorini, M. Enhancing automatic maritime surveillance systems with visual information. {\em IEEE Transactions On Intelligent Transportation Systems}. \textbf{18}, 824-833 (2016)
\bibitem{2019Thomopoulos2}Thomopoulos, S. Maritime situational awareness forensics tools for a Common Information Sharing Environment (CISE). {\em 2019 4th International Conference On Smart And Sustainable Technologies (SpliTech)}. (2019,6)
\bibitem{marinetrafficMarineTrafficGlobal}MarineTraffic MarineTraffic: Global Ship Tracking Intelligence | AIS Marine Traffic — marinetraffic.com. (marinetraffic.com), Accessed 29.01.2024.
\bibitem{aishubDispatcherFree}AISDispatcher AIS Dispatcher - free AIS data sharing tool | AISHub — aishub.net. (https://www.aishub.net/ais-dispatcher), Accessed 29.01.2024.
\bibitem{Kress2023-ua}Kress, M. \& Mitchell, K. AIS data : an overview of free sources. (Engineer Research,2023,2)
\bibitem{uscgHistoricalRequest}USCG AIS Historical Request Form | Navigation Center — navcen.uscg.gov. (https://www.navcen.uscg.gov/contact/ais-historical-request), Accessed 29.01.2024.
\bibitem{marinecadastreMarineCadastregovVessel}MarineCadastre MarineCadastre.gov | Vessel Traffic Data — marinecadastre.gov. (https://marinecadastre.gov/ais/), Accessed 29.01.2024.
\bibitem{dotSeaVision}SeaVision SeaVision — seavision.volpe.dot.gov. (https://seavision.volpe.dot.gov), Accessed 29.01.2024.
\bibitem{dotMSSISHome}MSSIS MSSIS: Home — mssis.volpe.dot.gov. (https://mssis.volpe.dot.gov/Main/index.html), Accessed 29.01.2024.
\bibitem{globalmaritimetrafficGlobalMaritime}MarineTraffic Global Maritime Traffic | Ship AIS Navigation Data \& Maps — globalmaritimetraffic.org. (https://globalmaritimetraffic.org/index.html), Accessed 29.01.2024.
\bibitem{arcgisVesseltraffic}LivingAtlas vessel-traffic — livingatlas.arcgis.com. (https://livingatlas.arcgis.com/vessel-traffic/), Accessed 29.01.2024.
\bibitem{radford2018network}Radford, B., Apolonio, L., Trias, A. \& Simpson, J. Network Traffic Anomaly Detection Using Recurrent Neural Networks. (2018)
\bibitem{2016Nanduri}Nanduri, A. \& Sherry, L. Anomaly detection in aircraft data using Recurrent Neural Networks (RNN). {\em Conference: 2016 Integrated Communications Navigation And Surveillance (ICNS)}. (2016,4)
\bibitem{fleetmonLiveVessel}Fleetmon Live AIS Vessel Tracker with Ship and Port Database — fleetmon.com. (https://www.fleetmon.com/), Accessed 29.01.2024.
\bibitem{hifleet}HiFleet HiFleet — hifleet.com. (https://www.hifleet.com/vessels/), Accessed 29.01.2024.
\bibitem{openstreetmapNominatimDemo}Nominatim Nominatim Demo — nominatim.openstreetmap.org. (https://nominatim.openstreetmap.org/ui/search.html), Accessed 29.01.2024.
\bibitem{2012Vespe}Vespe, M. \& Greidanus, H. SAR Image Quality Assessment and Indicators for Vessel and Oil Spill Detection. {\em IEEE Transactions On Geoscience And Remote Sensing}. \textbf{50}, 4726-4734 (2012)
\bibitem{2013Sermi}Sermi, F., Mugnai, C., Cuccoli, F. \& Facheris, L. Analysis of the radar coverage provided by a maritime Radar Network of Co-operative Vessels based on real AIS data. {\em 2013 European Radar Conference}. pp. 251-254 (2013)
\bibitem{2008Buck}Buck, H., Sharghi, E., Guilas, C., Stastny, J., Morgart, W., Schalcosky, B. \& Pifko, K. Enhanced ship detection from overhead imagery - art. no. 69450U. {\em Proceedings Of SPIE - The International Society For Optical Engineering}. (2008,5)
\bibitem{2015Shafer}Shafer, S., Harguess, J. \& Forero, P. Sparsity-driven anomaly detection for ship detection and tracking in maritime video. {\em Conference: SPIE Defense + Security}. pp. 947608 (2015,5)
\bibitem{chen2024ship}Chen, X., Wang, M., Ling, J., Wu, H., Wu, B. \& Li, C. Ship imaging trajectory extraction via an aggregated you only look once (YOLO) model. {\em Engineering Applications Of Artificial Intelligence}. \textbf{130} pp. 107742 (2024)
\bibitem{2010Horstmann}Horstmann, G., Schlick, T., Horstmann, J. \& Maresca, S. Evaluation of an HF-radar ship detection and tracking algorithm by comparison to AIS and SAR data. {\em 2010 International WaterSide Security Conference}. pp. 1-6 (2010)
\bibitem{2012Braca}Braca, P., Grasso, R., Vespe, M., Maresca, S. \& Horstmann, J. Application of the JPDA-UKF to HFSW radars for maritime situational awareness. {\em 2012 15th International Conference On Information Fusion}. pp. 2585-2592 (2012)
\bibitem{2005Griffiths}Griffiths, H. \& Baker, C. Passive coherent location radar systems. Part 1: Performance prediction. {\em Radar, Sonar And Navigation, IEE Proceedings -}. \textbf{152} pp. 153-159 (2005,7)
\bibitem{2014Langellotti}Langellotti, D., Colone, F., Lombardo, P., Tilli, E., Sedehi, M. \& Farina, A. Over the horizon maritime surveillance capability of DVB-T based Passive Radar. {\em 2014 44th European Microwave Conference}. pp. 509-512 (2014,10)
\bibitem{2015Papi}Papi, F., Tarchi, D., Vespe, M., Oliveri, F., Borghese, F., Aulicino, G. \& Vollero, A. Radiolocation and Tracking of Automatic Identification System Signals for Maritime Situational Awareness. {\em IET Radar Sonar \& Navigation}. (2015,6)
\bibitem{2019Wang}Wang, Y., Ning, X., Leng, B. \& Fu, H. Ship Detection Based on Deep Learning. {\em 2019 IEEE International Conference On Mechatronics And Automation (ICMA)}. pp. 275-279 (2019)
\bibitem{2022Verma}Verma, G., Gupta, A., Bansal, S. \& Dhiman, H. Monitoring Maritime Traffic with Ship Detection via YOLOv4. {\em 2022 2nd International Conference On Artificial Intelligence And Signal Processing (AISP)}. pp. 1-7 (2022)
\bibitem{2022Passah}Passah, A., Sur, S., Paul, B. \& Kandar, D. SAR Image Classification: A Comprehensive Study and Analysis. {\em IEEE Access}. \textbf{10} pp. 20385-20399 (2022)
\bibitem{2019Sudhir}Sudhir, K. Study of synthetic aperture radar and automatic identification system for ship target detection. {\em Journal Of Ocean Engineering And Science}. \textbf{4}, 173-182 (2019)
\bibitem{2021Liao}Liao, N., Datcu, M., Zhang, Z., Guo, W., Zhao, J. \& Yu, W. Analyzing the Separability of SAR Classification Dataset in Open Set Conditions. {\em IEEE Journal Of Selected Topics In Applied Earth Observations And Remote Sensing}. \textbf{14} pp. 7895-7910 (2021)
\bibitem{2019Babbar}Babbar, J. \& Rathee, N. Satellite Image Analysis: A Review. {\em 2019 IEEE International Conference On Electrical, Computer And Communication Technologies (ICECCT)}. pp. 1-6 (2019)
\bibitem{Auslander2012MaritimeTD}Auslander, B., Gupta, K. \& Aha, D. Maritime Threat Detection Using Probabilistic Graphical Models. {\em The Florida AI Research Society}. (2012)
\bibitem{kim2019anomalous}Kim, J., Lee, J. \& Kim, K. Anomalous Vessel Behavior Detection Based on SVR Seaway Model. {\em International Journal Of Fuzzy Logic And Intelligent Systems}. \textbf{19}, 18-27 (2019)
\bibitem{2016Kim}Kim, D., Kim, K., Park, G. \& Jeong, J. A Study on the Implementation of Intelligent Navigational Risk Assessment System for High-risk Vessel using IoT Sensor Gateway. {\em Journal Of Korean Institute Of Intelligent Systems}. \textbf{26} pp. 239-245 (2016,1)
\bibitem{2015Kim}Kim, J. \& Jeong, J. Pattern Recognition of Ship Navigational Data Using Support Vector Machine. {\em The International Journal Of Fuzzy Logic And Intelligent Systems}. \textbf{15} pp. 268-276 (2015,12)
\bibitem{2012Ng}Ng, G., Teow, L., Yong, K., Mui, S., Koh, A., Chong, W., Tan, K., Tan, Y. \& Toh, B. Technologies to aid decision making for maritime security. {\em 2012 15th International Conference On Information Fusion}. pp. 1637-1644 (2012)
\bibitem{2016Coraluppi}Coraluppi, S., Carthel, C., Braca, P. \& Millefiori, L. The Mixed Ornstein-Uhlenbeck Process and context exploitation in multi-target tracking. {\em 2016 19th International Conference On Information Fusion (FUSION)}. pp. 217-224 (2016)
\bibitem{2018Toloue}Toloue, K. \& Jahan, M. Anomalous behavior detection of marine vessels based on Hidden Markov Model. {\em 2018 6th Iranian Joint Congress On Fuzzy And Intelligent Systems (CFIS)}. pp. 10-12 (2018)
\bibitem{Mascaro2010LearningAV}Mascaro, S., Korb, K. \& Nicholson, A. Learning Abnormal Vessel Behaviour from AIS Data with Bayesian Networks at Two Time Scales. {\em Clayton School Of Information Technology, Monash University}. (2010)
\bibitem{Woodill2020PredictingIF}Woodill, A., Kavanaugh, M., Harte, M. \& Watson, J. Predicting Illegal Fishing on the Patagonia Shelf from Oceanographic Seascapes. {\em ArXiv}. \textbf{abs/2007.05470} (2020)
\bibitem{2014Castaldo}Castaldo, F., Palmieri, F., Bastani, V., Marcenaro, L. \& Regazzoni, C. Abnormal vessel behavior detection in port areas based on Dynamic Bayesian Networks. {\em 17th International Conference On Information Fusion (FUSION)}. pp. 1-7 (2014)
\bibitem{Ford2018LoiteringWI}Ford, J., Peel, D., Hardesty, B., Rosebrock, U. \& Wilcox, C. Loitering with intent - Catching the outlier vessels at sea. {\em PLoS ONE}. \textbf{13} (2018)
\bibitem{2018Ford}Ford, J., Peel, D., Kroodsma, D., Hardesty, B., Rosebrock, U. \& Wilcox, C. Detecting suspicious activities at sea based on anomalies in Automatic Identification Systems transmissions. {\em PLOS ONE}. \textbf{13} (2018,8)
\bibitem{2012Kowalska}Kowalska, K. \& Peel, L. Maritime anomaly detection using Gaussian Process active learning. {\em 2012 15th International Conference On Information Fusion}. pp. 1164-1171 (2012)
\bibitem{2010Lane}Lane, R., Nevell, D., Hayward, S. \& Beaney, T. Maritime anomaly detection and threat assessment. {\em 2010 13th International Conference On Information Fusion}. pp. 1-8 (2010)
\bibitem{Li2017ADR}Li, H., Liu, J., Liu, R., Xiong, N., Wu, K. \& Kim, T. A Dimensionality Reduction-Based Multi-Step Clustering Method for Robust Vessel Trajectory Analysis. {\em Sensors (Basel, Switzerland)}. \textbf{17} (2017)
\bibitem{MAZZARELLA2017110}Mazzarella, F., Vespe, M., Alessandrini, A., Tarchi, D., Aulicino, G. \& Vollero, A. A novel anomaly detection approach to identify intentional AIS on-off switching. {\em Expert Systems With Applications}. \textbf{78} pp. 110-123 (2017)
\bibitem{2013Pallotta2}Pallotta, G., Vespe, M. \& Bryan, K. Traffic Route Extraction and Anomaly Detection from AIS Data. {\em International COST MOVE Workshop On Moving Objects At Sea}. (2013,6)
\bibitem{2019Shahir}Shahir, A., Tayebi, M., Glässer, U., Charalampous, T., Zohrevand, Z. \& Wehn, H. Mining Vessel Trajectories for Illegal Fishing Detection. {\em 2019 IEEE International Conference On Big Data (Big Data)}. pp. 1917-1927 (2019)
\bibitem{2017Wang}Wang, G., Malik, A., Yau, C., Surakitbanharn, C. \& Ebert, D. TraSeer: A visual analytics tool for vessel movements in the coastal areas. {\em 2017 IEEE International Symposium On Technologies For Homeland Security (HST)}. pp. 1-6 (2017,4)
\bibitem{2020Xia}Xia, Z. \& Gao, S. Analysis of Vessel Anomalous Behavior Based on Bayesian Recurrent Neural Network. {\em 2020 IEEE 5th International Conference On Cloud Computing And Big Data Analytics (ICCCBDA)}. pp. 393-397 (2020)
\bibitem{2017Zhen}Zhen, R., Yongxing, J., Hu, Q., Shao, Z. \& Nikitakos, N. Maritime Anomaly Detection within Coastal Waters Based on Vessel Trajectory Clustering and Naïve Bayes Classifier. {\em Journal Of Navigation}. \textbf{70} pp. 1-23 (2017,1)
\bibitem{2015FernandezArguedas}Fernandez Arguedas, V., Mazzarella, F. \& Vespe, M. Spatio-temporal data mining for maritime situational awareness. {\em OCEANS 2015 - Genova}. pp. 1-8 (2015)
\bibitem{2021Pedroche}Pedroche, D., Herrero, D., Herrero, J. \& Lopez, J. Clustering of maritime trajectories with AIS features for context learning. {\em 2021 IEEE 24th International Conference On Information Fusion (FUSION)}. (2021,11)
\bibitem{2021Botts}Botts, C. A Novel Metric for Detecting Anomalous Ship Behavior Using a Variation of the DBSCAN Clustering Algorithm. {\em SN Computer Science}. \textbf{2} (2021,8)
\bibitem{2023Li}Li, J., Liu, J., Zhang, X., Li, X., Wang, J. \& Wu, Z. A Novel Hybrid Approach for Detecting Abnormal Vessel Behavior in Maritime Traffic. {\em 2023 7th International Conference On Transportation Information And Safety (ICTIS)}. (2023,8)
\bibitem{2020Wang2}Wang, F., Lei, Y., Liu, Z., Wang, X., Ji, S. \& Tung, A. Fast and parameter-light rare behavior detection in maritime trajectories. {\em Information Processing \& Management}. \textbf{57}, 102268 (2020,9)
\bibitem{2020Liu}Liu, D. \& Shi, G. Ship Collision Risk Assessment Based on Collision Detection Algorithm. {\em IEEE Access}. \textbf{8} (2020)
\bibitem{2023Pohontu}Pohontu, A., Nedelcu, L. \& Vertan, C. Fitting Empirical Distributions for Vessels Behavioural Analysis and Maritime Anomaly Detection. {\em 2023 17th International Conference On Engineering Of Modern Electric Systems (EMES)}. (2023,6)
\bibitem{2023Pohontu1}Pohontu, A., Gheorghe, R. \& Vertan, C. Outlier Detection Approach for Discovering Anomalous Maritime Profiles. {\em 2023 15th International Conference On Electronics, Computers And Artificial Intelligence (ECAI)}. (2023,6)
\bibitem{2015Sun}Sun, F., Deng, Y., Deng, F., Zhu, Q. \& Chu, H. Unsupervised maritime traffic pattern extraction from spatio-temporal data. {\em 2015 11th International Conference On Natural Computation (ICNC)}. pp. 1218-1223 (2015)
\bibitem{2022Szarmach}Szarmach, M. \& Czarnowski, I. Multi-Label Classification for AIS Data Anomaly Detection Using Wavelet Transform. {\em IEEE Access}. \textbf{10} pp. 109119-109131 (2022)
\bibitem{handayani2015anomaly}Handayani, D., Sediono, W. \& Shah, A. ANOMALY DETECTION IN VESSEL TRACKING–A BAYESIAN NETWORKS (BNs) APPROACH. {\em International Journal Of Maritime Engineering}. \textbf{157} (2015)
\bibitem{2017Duca}Duca, A., Bacciu, C. \& Marchetti, A. A K-nearest neighbor classifier for ship route prediction. {\em OCEANS 2017 - Aberdeen}. pp. 1-6 (2017)
\bibitem{2018Coscia}Coscia, P., Braca, P., Millefiori, L., Palmieri, F. \& Willett, P. Multiple Ornstein-Uhlenbeck Processes for Maritime Traffic Graph Representation. {\em IEEE Transactions On Aerospace And Electronic Systems}. \textbf{54}, 2158-2170 (2018)
\bibitem{2018Coscia1}Coscia, P., Palmieri, F., Braca, P., Millefiori, L. \& Willett, P. Unsupervised Maritime Traffic Graph Learning with Mean-Reverting Stochastic Processes. {\em 2018 21st International Conference On Information Fusion (FUSION)}. (2018,7)
\bibitem{2020Singh1}Singh, S. \& Heymann, F. On the Effectiveness of AI-Assisted Anomaly Detection Methods in Maritime Navigation. {\em 2020 IEEE 23rd International Conference On Information Fusion (FUSION)}. (2020,7)
\bibitem{2015Pallotta}Pallotta, G. \& Jousselme, A. Data-driven detection and context-based classification of maritime anomalies. {\em 2015 18th International Conference On Information Fusion (Fusion)}. pp. 1152-1159 (2015)
\bibitem{2019Han}Han, K., Chiu, C. \& Chien, W. The Application of Support Vector Machine (SVM) on the Sentiment Analysis of Internet Posts. {\em 2019 IEEE Eurasia Conference On IOT, Communication And Engineering (ECICE)}. pp. 154-155 (2019)
\bibitem{2019Hanyang}Hanyang, Z., Xin, S. \& Zhenguo, Y. Vessel Sailing Patterns Analysis from S-AIS Data Dased on K-means Clustering Algorithm. {\em 2019 IEEE 4th International Conference On Big Data Analytics (ICBDA)}. (2019,3)
\bibitem{2014Shahir}Shahir, H., Glässer, U., Nalbandyan, N. \& Wehn, H. Maritime Situation Analysis: A Multi-vessel Interaction and Anomaly Detection Framework. {\em 2014 IEEE Joint Intelligence And Security Informatics Conference}. pp. 192-199 (2014)
\bibitem{2023Hu}Hu, J., Kaur, K., Lin, H., Wang, X., Hassan, M., Razzak, I. \& Hammoudeh, M. Intelligent Anomaly Detection of Trajectories for IoT Empowered Maritime Transportation Systems. {\em IEEE Transactions On Intelligent Transportation Systems}. (2023)
\bibitem{2014FernandezArguedas}Fernandez Arguedas, V., Pallotta, G. \& Vespe, M. Unsupervised Maritime Pattern Analysis to Enhance Contextual Awareness. {\em Context-Awareness In Geographic Information Services (CAGIS 2014)At: Wien}. (2014,9)
\bibitem{2016Millefiori}Millefiori, L., Braca, P., Bryan, K. \& Willett, P. Modeling Vessel Kinematics Using a Stochastic Mean-Reverting Process for Long-Term Prediction. {\em IEEE Transactions On Aerospace And Electronic Systems}. \textbf{52} (2016,10)
\bibitem{2021Prasad}Prasad, P., Vatsal, V. \& Roy Chowdhury, R. Maritime Vessel Route Extraction and Automatic Information System (AIS) Spoofing Detection. {\em 2021 International Conference On Advances In Electrical, Computing, Communication And Sustainable Technologies (ICAECT)}. (2021,2)
\bibitem{2017Fu}Fu, P., Wang, H., Liu, K., Hu, X. \& Zhang, H. Finding Abnormal Vessel Trajectories Using Feature Learning. {\em IEEE Access}. \textbf{5} pp. 7898-7909 (2017)
\bibitem{2015Cazzanti}Cazzanti, L. \& Pallotta, G. Mining maritime vessel traffic: Promises, challenges, techniques. {\em OCEANS 2015 - Genova}. pp. 1-6 (2015)
\bibitem{2021dAfflisio}D'Afflisio, E., Braca, P., Chisci, L., Battistelli, G. \& Willett, P. Maritime Anomaly Detection of Malicious Data Spoofing and Stealth Deviations from Nominal Route Exploiting Heterogeneous Sources of Information. {\em 2021 IEEE 24th International Conference On Information Fusion (FUSION)}. (2021,11)
\bibitem{2018Lei}Lei, B. \& Mingchao, D. A distance-based trajectory outlier detection method on maritime traffic data. {\em 2018 4th International Conference On Control, Automation And Robotics (ICCAR)}. (2018,4)
\bibitem{2014DuToit}Du Toit, J. \& Van Vuuren, J. Semi-automated maritime vessel activity detection using hidden Markov models. {\em Proceedings Of The 43rd Annual Conference Of The Operations Research Society Of South Africa}. pp. 72-78 (2014)
\bibitem{2014Pallotta}Pallotta, G., Horn, S., Braca, P. \& Bryan, K. Context-enhanced vessel prediction based on Ornstein-Uhlenbeck processes using historical AIS traffic patterns: Real-world experimental results. {\em 17th International Conference On Information Fusion (FUSION)}. pp. 1-7 (2014)
\bibitem{2023Xie}Xie, L., Guo, T., Chang, J., Wan, C., Hu, X., Yang, Y. \& Ou, C. A Novel Model for Ship Trajectory Anomaly Detection Based on Gaussian Mixture Variational Autoencoder. {\em IEEE Transactions On Vehicular Technology}. (2023)
\bibitem{2021dAfflisio1}D'Afflisio, E., Braca, P. \& Willett, P. Malicious AIS Spoofing and Abnormal Stealth Deviations: A Comprehensive Statistical Framework for Maritime Anomaly Detection. {\em IEEE Transactions On Aerospace And Electronic Systems}. \textbf{57} (2021,8)
\bibitem{2019Huang1}Huang, Y. \& Zhang, Q. Identification of anomaly behavior of ships based on KNN and LOF combination algorithm. {\em AIP Conference Proceedings}. (2019)
\bibitem{2018Virjonen}Virjonen, P., Nevalainen, P., Pahikkala, T. \& Heikkonen, J. Ship Movement Prediction Using k-NN Method. {\em 2018 Baltic Geodetic Congress (BGC Geomatics)}. pp. 304-309 (2018)
\bibitem{2018Cai}Cai, C., Chen, R., Liu, A., Roberts, F. \& Xie, M. iGroup Learning and iDetect for Dynamic Anomaly Detection with Applications in Maritime Threat Detection. {\em 2018 IEEE International Symposium On Technologies For Homeland Security (HST)}. pp. 1-6 (2018)
\bibitem{2016Souza}Souza, E., Boerder, K. \& Worm, B. Improving Fishing Pattern Detection from Satellite AIS Using Data Mining and Machine Learning. {\em PLOS ONE}. \textbf{11} (2016,7)
\bibitem{jiang2017partition}Jiang, X., Souza, E., Liu, X., Soleimani, B., Wang, X., Silver, D. \& Matwin, S. Partition-wise Recurrent Neural Networks for Point-based AIS Trajectory Classification.. {\em ESANN}. (2017)
\bibitem{2010Laxhammar}Laxhammar, R. \& Falkman, G. Conformal prediction for distribution-independent anomaly detection in streaming vessel data. {\em Proceedings Of The ACM SIGKDD International Conference On Knowledge Discovery And Data Mining}. (2010,7)
\bibitem{2010Willems}Willems, N., Hage, W., Vries, G., Janssens, J. \& Malaisé, V. An integrated approach for visual analysis of a multi-source moving objects knowledge base. {\em International Journal Of Geographical Information Science}. \textbf{9} pp. 53-1 (2010,10)
\bibitem{2012Willems}Willems, N., Scheepens, R., Wetering, H. \& Wijk, J. Visualization of Vessel Traffic. {\em Situation Awareness With Systems Of Systems}. pp. 73-87 (2012,10)
\bibitem{2011Lane}Lane, R. Maritime route anomaly detection. {\em AD 2011 Workshop Proceedings}. pp. 123 (2011)
\bibitem{2017Zor}Zor, C. \& Kittler, J. Maritime anomaly detection in ferry tracks. {\em 2017 IEEE International Conference On Acoustics, Speech And Signal Processing (ICASSP)}. pp. 2647-2651 (2017)
\bibitem{Hayes2015}Hayes, M. \& Capretz, M. Contextual anomaly detection framework for big sensor data. {\em Journal Of Big Data}. \textbf{2}, 2 (2015,2),
\bibitem{2017Patroumpas}Patroumpas, K., Alevizos, E., Artikis, A., Vodas, M., Pelekis, N. \& Theodoridis, Y. Online Event Recognition from Moving Vessel Trajectories. {\em GeoInformatica}. \textbf{21} (2017,4)
\bibitem{2017Keane}Keane, K. Detecting Motion Anomalies. {\em Proceedings Of The 8th ACM SIGSPATIAL Workshop On GeoStreaming}. pp. 21-28 (2017)
\bibitem{2013Katsilieris}Katsilieris, F., Braca, P. \& Coraluppi, S. Detection of malicious AIS position spoofing by exploiting radar information. {\em Proceedings Of The 16th International Conference On Information Fusion}. pp. 1196-1203 (2013)
\bibitem{2016Mazzarella}Mazzarella, F., Vespe, M., Tarchi, D., Aulicino, G. \& Vollero, A. AIS reception characterisation for AIS on/off anomaly detection. {\em 2016 19th International Conference On Information Fusion (FUSION)}. pp. 1867-1873 (2016)
\bibitem{2018Dobrkovic}Dobrkovic, A., Iacob, M. \& Hillegersberg, J. Maritime pattern extraction and route reconstruction from incomplete AIS data. {\em International Journal Of Data Science And Analytics}. \textbf{5} (2018,3)
\bibitem{2022Soldani}Soldani, M., Faggioni, O., Zunino, R., Carbone, A. \& Gemma, M. The LAMA system: A "smart" magnetometer network for harbour protection. {\em Journal Of Applied Geophysics}. \textbf{204} pp. 104743 (2022,9)
\bibitem{2012Snidaro}Snidaro, L., Visentini, I., Bryan, K. \& Foresti, G. Markov Logic Networks for context integration and situation assessment in maritime domain. {\em 2012 15th International Conference On Information Fusion}. pp. 1534-1539 (2012)
\bibitem{2020Belhadi}Belhadi, A., Djenouri, Y., Lin, J. \& Cano, A. Trajectory Outlier Detection. {\em ACM Transactions On Management Information Systems}. \textbf{11} (2020,6)
\bibitem{2023Wang4}Wang, Y., Liu, J., Liu, R., Liu, Y. \& Yuan, Z. Data-driven methods for detection of abnormal ship behavior: Progress and trends. {\em Ocean Engineering}. \textbf{271} pp. 113673 (2023,3)
\bibitem{2016Singh}Singh, A., Aggarwal, V. \& Tiwari, P. Coastal surveillance in multi sensor environment: A design approach. {\em 2016 3rd International Conference On Recent Advances In Information Technology (RAIT)}. pp. 1-6 (2016,3)
\bibitem{chen2024autonomous}Chen, X., Liu, S., Zhao, J., Wu, H., Xian, J. \& Montewka, J. Autonomous port management based AGV path planning and optimization via an ensemble reinforcement learning framework. {\em Ocean \& Coastal Management}. \textbf{251} pp. 107087 (2024)
\bibitem{2019Ghosh}Ghosh, S., Dasgupta, A. \& Swetapadma, A. A Study on Support Vector Machine based Linear and Non-Linear Pattern Classification. {\em 2019 International Conference On Intelligent Sustainable Systems (ICISS)}. pp. 24-28 (2019)
\bibitem{Bishop-2016}Bishop, C. Pattern Recognition and Machine Learning, ser. Information Science and Statistics. (New York: Springer-Verlag,2016)
\bibitem{Mirghasemi2013APA}Mirghasemi, S. A Parallel Approach to Combine SVM, Edge and Corner Detection Methods for Target Detection. {\em J. Multim. Process. Technol.}. \textbf{4} pp. 47-54 (2013)
\bibitem{2006Li}Li, X., Han, J. \& Kim, S. Motion-Alert: Automatic Anomaly Detection in Massive Moving Objects. {\em Intelligence And Security Informatics, IEEE International Conference On Intelligence And Security Informatics, ISI 2006, San Diego, CA, USA, May 23-24, 2006, Proceedings}. pp. 166-177 (2006,5)
\bibitem{2010Keim}Keim, D., Mansmann, F. \& Thomas, J. Visual Analytics: How Much Visualization and How Much Analytics?. {\em SIGKDD Explor. Newsl.}. \textbf{11}, 5-8 (2010,5)
\bibitem{2014Karamizadeh}Karamizadeh, S., Abdullah, S., Halimi, M., Shayan, J. \& Rajabi, M. Advantage and drawback of support vector machine functionality. {\em 2014 International Conference On Computer, Communications, And Control Technology (I4CT)}. pp. 63-65 (2014)
\bibitem{2016Hu}Hu, W., Sun, Y., Li, X., Jiang, Y. \& Yu, M. Cam-shift target tracking approach based on back projection method with distance weights. {\em 2016 International Conference On Wavelet Analysis And Pattern Recognition (ICWAPR)}. pp. 252-257 (2016)
\bibitem{2015Khanna}Khanna, R. \& Awad, M. Support vector regression. {\em Efficient Learning Machines: Theories, Concepts, And Applications For Engineers And System Designers}. pp. 67-80 (2015,4)
\bibitem{2015Shaily}Shaily, S. \& Mangat, V. The Hidden Markov Model and its application to Human Activity Recognition. {\em 2015 2nd International Conference On Recent Advances In Engineering \& Computational Sciences (RAECS)}. pp. 1-4 (2015)
\bibitem{Franzese2019HiddenMM}Franzese, M. \& Iuliano, A. Hidden Markov Models. {\em Encyclopedia Of Bioinformatics And Computational Biology}. pp. 753-762 (2019)
\bibitem{2004Franke}Franke, A., Caelli, T. \& Hudson, R. Analysis of movements and behavior of caribou (Rangifer tarandus) using hidden Markov models. {\em Ecological Modelling}. \textbf{173} pp. 259-270 (2004,4)
\bibitem{2009Guo}Guo, Y., Poulton, G., Corke, P., Bishop Hurley, G., Wark, T. \& Swain, D. Using accelerometer, high sample rate GPS and magnetometer data to develop a cattle movement and behaviour model. {\em Ecological Modelling}. \textbf{220} pp. 2068-2075 (2009,9)
\bibitem{2017Mohammed}Mohammed, N. \& Abdulazeez, A. Gene clustering with partition around medoids algorithm based on weighted and normalized mahalanobis distance. {\em 2017 International Conference On Intelligent Informatics And Biomedical Sciences (ICIIBMS)}. pp. 140-145 (2017)
\bibitem{2014Mishra}Mishra, M. \& Srivastava, M. A view of Artificial Neural Network. {\em 2014 International Conference On Advances In Engineering \& Technology Research (ICAETR - 2014)}. pp. 1-3 (2014)
\bibitem{2017Albawi}Albawi, S., Mohammed, T. \& Al Zawi, S. Understanding of a convolutional neural network. {\em 2017 International Conference On Engineering And Technology (ICET)}. pp. 1-6 (2017)
\bibitem{2020Soloviev}Soloviev, V., Farahnakian, F., Zelioli, L., Iancu, B., Lilius, J. \& Heikkonen, J. Comparing CNN-Based Object Detectors on Two Novel Maritime Datasets. {\em 2020 IEEE International Conference On Multimedia \& Expo Workshops (ICMEW)}. pp. 1-6 (2020)
\bibitem{2016Fraccaro}Fraccaro, M., Sønderby, S., Paquet, U. \& Winther, O. Sequential Neural Models with Stochastic Layers. {\em 30th Conference On Neural Information Processing Systems (NIPS 2016), Barcelona, Spain}. (2016,5)
\bibitem{2017Maddison}Maddison, C., Lawson, J., Tucker, G., Heess, N., Norouzi, M., Mnih, A., Doucet, A. \& Teh, Y. Filtering Variational Objectives. {\em Advances In Neural Information Processing Systems}. \textbf{30} (2017)
\bibitem{Chung2015ARL}Chung, J., Kastner, K., Dinh, L., Goel, K., Courville, A. \& Bengio, Y. A Recurrent Latent Variable Model for Sequential Data. {\em Neural Information Processing Systems}. (2015)
\bibitem{2015Malhotra}Malhotra, P., Vig, L., Shroff, G. \& Agarwal, P. Long Short Term Memory Networks for Anomaly Detection in Time Series. {\em 23rd European Symposium On Artificial Neural Networks, Computational Intelligence And Machine Learning, ESANN 2015, Bruges, Belgium}. (2015,4)
\bibitem{2022Nalavade}Nalavade, J. \& Sanjay, P. Driver Drowsiness Detection System Using Deep Neural Network. {\em 2022 3rd International Conference On Computing, Analytics And Networks (ICAN)}. pp. 1-4 (2022)
\bibitem{Rezk2019RecurrentNN}Rezk, N., Purnaprajna, M., Nordstrom, T. \& Ul Abdin, Z. Recurrent Neural Networks: An Embedded Computing Perspective. {\em IEEE Access}. \textbf{8} pp. 57967-57996 (2019)
\bibitem{2018Lv}Lv, J., Li, Q., Sun, Q. \& Wang, X. T-CONV: A Convolutional Neural Network for Multi-scale Taxi Trajectory Prediction. {\em 2018 IEEE International Conference On Big Data And Smart Computing (BigComp)}. pp. 82-89 (2018,7)
\bibitem{DABIRI2018360}Dabiri, S. \& Heaslip, K. Inferring transportation modes from GPS trajectories using a convolutional neural network. {\em Transportation Research Part C: Emerging Technologies}. \textbf{86} pp. 360-371 (2018)
\bibitem{2014Wang}Wang, X., Liu, X., Liu, B., Souza, E. \& Matwin, S. Vessel route anomaly detection with Hadoop MapReduce. {\em 2014 IEEE International Conference On Big Data (Big Data)}. pp. 25-30 (2014)
\bibitem{2000Stephenson}Stephenson, T. An introduction to Bayesian network theory and usage. (Idiap,2000)
\bibitem{barber2012}Barber, D. Bayesian Reasoning and Machine Learning. (Cambridge University Press,2012)
\bibitem{2012Smith}Smith, M., Reece, S., Roberts, S. \& Rezek, I. Online Maritime Abnormality Detection Using Gaussian Processes and Extreme Value Theory. {\em 2012 IEEE 12th International Conference On Data Mining}. (2012,12)
\bibitem{2013Smith}Smith, M., Reece, S., Roberts, S., Psorakis, I. \& Rezek, I. Maritime abnormality detection using Gaussian processes. {\em Knowledge And Information Systems}. \textbf{38} (2013,8)
\bibitem{2018Anneken}Anneken, M., Jousselme, A., Robert, S. \& Beyerer, J. Synthetic Trajectory Extraction for Maritime Anomaly Detection. {\em 2018 International Conference On Computational Science And Computational Intelligence (CSCI)}. (2018,12)
\bibitem{2021Wang}Wang, P., Zhang, Y. \& Jiang, W. Application of K-Nearest Neighbor (KNN) Algorithm for Human Action Recognition. {\em 2021 IEEE 4th Advanced Information Management, Communicates, Electronic And Automation Control Conference (IMCEC)}. \textbf{4} pp. 492-496 (2021)
\bibitem{2019Taunk}Taunk, K., De, S., Verma, S. \& Swetapadma, A. A Brief Review of Nearest Neighbor Algorithm for Learning and Classification. {\em 2019 International Conference On Intelligent Computing And Control Systems (ICCS)}. pp. 1255-1260 (2019)
\bibitem{2010Brax}Brax, C., Karlsson, A., Andler, S., Johansson, R. \& Niklasson, L. Evaluating precise and imprecise State-Based Anomaly detectors for maritime surveillance. {\em 2010 13th International Conference On Information Fusion}. (2010,7)
\bibitem{2019Chatzikokolakis}Chatzikokolakis, K., Zissis, D., Vodas, M., Spiliopoulos, G. \& Kontopoulos, I. A distributed lightning fast maritime anomaly detection service. {\em OCEANS 2019 - Marseille}. (2019,6)
\bibitem{Ester1996ADA}Ester, M., Kriegel, H., Sander, J. \& Xu, X. A Density-Based Algorithm for Discovering Clusters in Large Spatial Databases with Noise. {\em Knowledge Discovery And Data Mining}. (1996)
\bibitem{Khan2004RealtimePO}Khan, A., Bil, C., Marion, K. \& Crozier, M. Real-time prediction of ship motion and attitude using advanced prediction techniques. {\em 24th International Congress Of The Aeronautical Sciences}. (2004)
\bibitem{2013Guillarme}La Guillarme, N. \& Lerouvreur, X. Unsupervised extraction of knowledge from S-AIS data for maritime situational awareness. {\em Proceedings Of The 16th International Conference On Information Fusion}. pp. 2025-2032 (2013)
\bibitem{2011Laxhammar}Laxhammar, R. Anomaly detection in trajectory data for surveillance applications. (Örebro universitet,2011)
\bibitem{Vries2013}Vries, G. \& Someren, M. Recognizing Vessel Movements from Historical Data. {\em Situation Awareness With Systems Of Systems}. pp. 105-118 (2013)
\bibitem{2015Liu}Liu, B., Souza, E., Hilliard, C. \& Matwin, S. Ship movement anomaly detection using specialized distance measures. {\em 2015 18th International Conference On Information Fusion (Fusion)}. pp. 1113-1120 (2015)
\bibitem{2015LeCun}LeCun, Y., Bengio, Y. \& Hinton, G. Deep Learning. {\em Nature}. \textbf{521} pp. 436-44 (2015,5)
